\documentclass{article}
\usepackage[margin=1in]{geometry}
\usepackage{enumitem}
\usepackage{hyperref}

\begin{document}

\begin{center}
    \textbf{\Large Zifan Hua}
\end{center}

\section*{Contact Information}
\begin{itemize}[leftmargin=*]
    \item Email: \href{mailto:huazifan@gmail.com}{huazifan@gmail.com}
    \item Phone: +44 787 367 6711
    \item GitHub: \href{https://github.com/Alex222222222222}{https://github.com/Alex222222222222}
\end{itemize}

\section*{Summary}
As a highly motivated and detail-oriented individual with a strong background in mathematics and programming, I am excited to apply for the quantitative trader internship position for Jane Street. 
My experience in participating and winning in mathematics competitions demonstrates my ability to think critically and solve complex problems under pressure.
Additionally my experience in developing and maintaining open source projects demonstrates my ability to work independently and collaborate with others and also my programming skills.
I am eager to apply my skills and knowledge to contribute to the success of the trading team and learn from experienced professionals in the field.

\section*{Education}
\textbf{2021-2023, University of Nottingham Ningbo China}
\begin{itemize}
    \item \textbf{Relevant Coursework}
    \begin{itemize}
        \item Python Coursework
        \item Matlab Coursework
        \item Statistic Coursework
    \end{itemize}
    \item \textbf{Honours \& Awards}
    \begin{itemize}
        \item 2022, UNNC Mathematics Olympiad, Gold Medal
        \item 2022, IMC(International Mathematics Competition), Silver Medal
        \item 2023, UNNC Mathematics Olympiad, Gold Medal
        \item 2023, IMC(International Mathematics Competition), Gold Medal
    \end{itemize}
    \item \textbf{Clubs \& Activities}
    \begin{itemize}
        \item 2022-2023, UNNC Undergraduate Mathematics Seminar, Presenter
        \item 2022-2023, UNNC Cube Club, Society Leader
    \end{itemize}
\end{itemize}

\section*{Experience}
\textbf{2023, Personal Project}, MacOS Clipboard Manager
\begin{itemize}
    \item \textbf{Description}
    \begin{itemize}
        \item A clipboard manager for MacOS, written in Rust(Tauri+Yew+Sqlite).
        \item History search and filter with regular expression or fuzzy search.
    \end{itemize}
    \item \textbf{Skills}
    \begin{itemize}
        \item Rust
        \item Tauri(GUI Framework)
        \item Yew(Frontend)
        \item Database
    \end{itemize}
    \item \textbf{\href{https://github.com/Alex222222222222/CopyClip}{GitHub https://github.com/Alex222222222222/CopyClip}}
\end{itemize}
\textbf{2023, Personal Project}, Rust Library for 2FA
\begin{itemize}
    \item \textbf{Description}
    \begin{itemize}
        \item A Rust library for generating 2FA(Two Factor Authentication) codes.
        \item Support TOTP and HOTP.
        \item Support SHA1, SHA256, SHA512.
    \end{itemize}
    \item \textbf{Skills}
    \begin{itemize}
        \item Rust
        \item Cryptography
    \end{itemize}
    \item \textbf{\href{https://github.com/Alex222222222222/r2fa}{GitHub https://github.com/Alex222222222222/r2fa}}
\end{itemize}
\textbf{2022-2023, Society Leader}, UNNC Cube Club
\begin{itemize}
    \item \textbf{Description}
    \begin{itemize}
        \item Organize weekly meetings.
        \item Organize competitions and tutorial sessions.
    \end{itemize}
    \item \textbf{Skills}
    \begin{itemize}
        \item Leadership
        \item Communication
    \end{itemize}
\end{itemize}

\section*{Skills}
\begin{itemize}[leftmargin=*]
    \item \textbf{Mathematics}
    \item \textbf{Technical Skills}
    \begin{itemize}
        \item Rust
        \item Golang
        \item Python
        \item Matlab
        \item Database
    \end{itemize}
    \item \textbf{Tools}
    \begin{itemize}
        \item Git
        \item Linux
        \item Docker
        \item \LaTeX
    \end{itemize}
    \item \textbf{Languages}
    \begin{itemize}
        \item English
        \item Chinese
    \end{itemize}
    \item \textbf{Other}
    \begin{itemize}
        \item Communication
        \item Organization
    \end{itemize}
\end{itemize}

\end{document}